A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-04 rebuttal2_responses_revision2.tex

\subsection*{3-1}
Comments from the reviewer \#3

Round 1:
%Must be improved:
%Is the research design appropriate?
%Are the results clearly presented?
Are the conclusions supported by the results?

Only computer computing in this research to support 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of OS.

There is little information provided. The authors should provide more evidence to support this article.

Round 2:
The authors still did not provide any experiment results that support the finding of the manuscript.
%  Once the authors identify TMSB4X as a target, the rest of the analysis seems fine, but their rationale for looking into TMSB4X is not strongly supported by the available data.

@@

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comment and apology for inadequate evidence provided. 
We then did experiment for mRNA expression among HNSCC cell lysates to provide more evidence below to support our discovery of those candidate genes. We modified "Material and Methods" , Results and Discussion of manuscript according the new evidence.

\subsubsection*{Material and Methods}
Quantitative real-time PCR (qRT-PCR) analysis
\subsectionmark*{qRT-PCR analysis}

DKK1 mRNA expression in Hep-2 and 293T cell lines, as well as tumor tissues from 30 pairs of LSCC specimens and adjacent non-cancer specimens, were measured using qRT-PCR as described previously [3]. The primer sequences were as follows: DKK1 forward primer: 5'-TAGAGTCTAGAACGCAAGGATCT-3' and DKK1 reverse primer: 5'-CAAAAACTATCACAGCCTAAAGGG--3'; $\beta$-actin forward primer: 5'-TTGTTACAG GAAG TCCCTTGC C-3' and $\beta$-actin reverse primer: 5'-ATGCTATCACCTCCCC TGTGTG-3'. Relative mRNA levels were calculated based on the cycle threshold (Ct) values, according to the equation: 2–ÎCt [ÎCt = Ct (DKK1) – Ct (β-actin)]. 
All experiments were performed in triplicate.\cite{Shi2014}

\subsubsection*{Results}

\subsubsection*{Discussion}

\subsectionmark*{qPCR}

@@

%\subsubsection*{GSE2837} % non-TCGA
% from Anwser2-2
%by GEO GSE2837 HNSCC dataset (PrognoScan)
We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.\\bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
The GSE2837 carries % VUMC, VAMC, UTMDACC (1992-2005)
relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
The survival significance (Kaplan Meier P-value) is in the following probes of 10 genes:\\
1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
%17 out of 20 candidates
%?DKK1 (0.253635), 
Please see Supplementary Figure S3. %\ref{figure:fig_GSE2837}.
Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.

\subsubsubsection*{Review articles}
After discovering using our workflow, we also performed the literature review by Embase/Pubmed to find the evidence convincing to 7 of our suggested 20 biomarkers in cancer research.
%Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
%through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
%PubTator Central\cite{Wei2019} is a useful Pubmed text miner

%%%%%% bad guy
The Dickkopf1 (DKK1) gene encodes a protein mainly involved in Wnt and other signaling pathways.
Inhibition of DKK1 in Hep-2 cells reduces their proliferation, colony formation, cell migration, and invasion in vitro\cite{Shi2014}. %quantitative real-time PCR and western blot analyses
Pang et al.\cite{Pang2018} demonstrated that upregulation of DKK1 in SBC-3 cells (human small cell lung cancer) enhanced their proliferation, colony formation, cell migration, and invasion in vitro, as well as bone metastasis in vivo. 
Increased DKK1 levels in HNSCC tissues correlated with elevated VEGF-C and beta-catenin\cite{Shi2014}.
DKK1 expression was significantly associated with smoking, alcohol abuse, sex, human papillomavirus status\cite{Chakraborty2020}, tumor site, tumor invasion, and pathologic stage in HNSCC patients.\cite{Gao2018}.
The mRNA expression of DKK1 and DKK3 was elevated in human papillomavirus (HPV)-negative HNSCC\cite{Hu2020}. Overexpression of DKK1 indicates adverse OS in bladder urothelial carcinoma (BLCA)\cite{Wei2020}, HNSCC\cite{Chakraborty2020}\cite{Hu2020}\cite{Wei2020}, and pancreatic adenocarcinoma (PAAD)\cite{Wei2020}. %Moreover, DKK1 is increased in HPV\+ HNSCC, leading to the worst prognosis of the patients. 
%\cite{Shi2014}\cite{Gao2018}\cite{Chakraborty2020}(non-TCGA)\cite{Hu2020}\cite{Wei2020}
%Wei et al\cite{Wei2020} conducted the analysis of prognostic value of DKK1 expression in human cancers based on bioinformatics tools, including UALCAN, GEPIA2 (dataset from TCGA)\cite{Tang2019}, and DriverDBv3 databases.
%using http://gepia2.cancer-pku.cn/detail.php?gene=DKK1 => \cite{Tang2019}
%GEPIA is a commonly used interactive website that plots expression profiles of given genes (from TCGA database)

@@

%STC2:
The miR-381 suppresses cell proliferation, migration, and invasion in the HNSCC SCC-4 cell line through targeting stanniocalcin 2 (STC2) and participates in HNSCC development probably via the FAK/PI3K/Akt/mTOR signaling pathway.\cite{Ma2020}

% PGK1
Phosphoglycerate kinase 1 (PGK1 or PGK-1), a glycolysis enzyme, is responsive in cisplatin-resistant HNSCC cell line (H-1R). The resistance is associated with up-regulated expression of ATP-binding cassette transporter genes (MDR1, MRP1, and MRP2), CD55, and PGK1 and down-regulated expression Caveolin 1\cite{Nakamura2005}.

%SURF4
Surfeit gene 4 (SURF4): patients with tumors (such as glioma, breast cancer, lymphoma, , pancreatic cancer, adrenocortical carcinoma, and sarcoma%; not HNSCC
) exhibiting high SURF4 expression had significantly shorter overall survival than low SURF4 expression. SURF4 can induce cellular transformation and cell migration in vitro and has increased tumor growth ability in vivo\cite{Kim2018a}.
%NIH/3T3 cells (Mus musculus, mouse), 293T cell
%Loss of contact inhibition leads to phenotypic changes and promotes foci formation in vitro
%http://www.canevolve.org/AnalysisResults/AnalysisResults.html
%web-based tools survival (not TCGA?)

% USP10 qPCR primer https://www.origene.com/catalog/gene-expression/qpcr-primer-pairs/hp208343/usp10-human-qpcr-primer-pair-nm_005153
Ubiquitin specific peptidase 10 (USP10), one of the autophagy-related genes (ARGs) may serve as a prognostic biomarker and target for in various human cancers, including epithelial ovarian cancer, colorectal cancer, and HNSCC\cite{Ren2020}.
Functional annotation - by gene set variation analysis (GSVA) and gene set enrichment analysis (GSEA) - revealed that USP10 has been significantly enriched in many critical pathways correlated with tumorigenesis of HNSCC, including the p53 pathway, IL2 STAT5 signaling, TGF beta signaling, and PI3K Ak mTOR signaling\cite{Ren2020}.
% 13 ARGs (GABARAPL1, ITGA3, USP10, ST13, MAPK9, PRKN, FADD, IKBKB, ITPR1, TP73, MAP2K7, CDKN2A, and EEF2K) with prognostic value were identified in HNSCC patients
%found at Human Protein Atlas dataset (HPA), TCGA, and (GSE6631): A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631. https://www.proteinatlas.org/ENSG00000103194-USP10/pathology/head+and+neck+cancer

@@

%FOXA2
Prognostic signature integrated of DNA methylation, gene expression, and clinical information provides a prognostic prediction value for HNSCC patients. 
FOXA2 is significantly associated with the poor prognosis of HNSCC through the studies of CpG-based DNA methylation and RNA expression approach\cite{Shen2017a}.
%32 HNSCC patients had both tumor and adjacent non-tumor tissue samples in TCGA cohort, which was used as the discovery set to identify differential methylation CpG sites.
%  + 0.0256 × cg03774514 FOXA2 => "+" coefficients; higher prognostic score was significantly associated with shorter survival in the training set; 
% https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=28852427
%A multi-stage screening strategy => univariate Cox regression was used to evaluate their association with overall survival in the training set, which identified 15 CpG sites with P < 0.05. Further, SIS analysis was performed to further screen out a stable probe combination. Seven of the 15 candidate CpGs were identified, including cg13495205, cg07110405, cg03774514, cg09137696, cg19655456, cg03146625, and cg21546671 (Fig. 2c, Additional file 1: Table S1), mapped to AJAP1, SHANK2, FOXA2, MT1A, ZNF570, HOXC4, and HOXB4, respectively. Using coefficients generated from Cox model, we calculated a prognostic score for each patient based on individualized values of the seven genes (Fig. 2d): prognostic score, methylation = 0.0054 × cg13495205 AJAP1  + 0.0318 × cg07110405 SHANK2 + 0.0256 × cg03774514 FOXA2  + 0.0063 × cg09137696 MT1A  + 0.0013 × cg19655456 ZNF570 − 0.0297 × cg03146625 HOXC4  − 0.0157 × cg21546671 HOXB4 .
%Association between gene expression and methylation. Left panels show correlation of a AJAP1, b SHANK2, c FOXA2, d MT1A, e ZNF570, f HOXC4, and g HOXB4 expression (X-axis) with methylation (Y-axis). Right panels show Kaplan-Meier survival plots of gene expression from the TCGA cohort.

% STIP1; non-TCGA
Stress-induced phosphoprotein 1 (STIP1, also known as HOP, P60, STI1), is increased
in the poor survival patients of ovarian cancer\cite{Chao2013}\cite{Cho2014}. 
The auto-antibody against STIP1 in serum could be a useful diagnostic biomarker for early-stage esophageal squamous cell carcinoma\cite{Xu2017}.
%STIP1 could bind to bind Hsp70 and Hsp90.

### 2021-02-07 revisonNote1_responses.tex
revision note 2: rebuttal for reviewer #3

\section*{Response to Reviewer 3 Comments}
%Response to Referees} % rebuttal
We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}). 
%Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.

\subsection*{Comments from the reviewer \#3}

Round 1:
%Must be improved:
%Is the research design appropriate?
%Are the results clearly presented?
Are the conclusions supported by the results?

@@

There is little information provided. The authors should provide more evidence to support this article.

Round 2:
The authors still did not provide any experiment results that support the finding of the manuscript.

@@

\subsection*{Revision notes: rebuttal}  
%Where the authors disagree with a reviewer, they must provide a clear response by a rebuttal if some of the reviewer’s comments cannot be revised. 
%動之以情，和氣誠懇地說明原委 https://www.mdpi.com/journal/cancers/instructions#editorial_procedure
% *** Alex: yes, please answer the reviewer politely 和氣誠懇地 and tell him that 
%in a respectful and considerate manner.
We appreciate the reviewer for the critical comment and apology for short of experiment results. 
%We modified "Material and Methods",  Results and Discussion of manuscript according the new evidence.
It is encouraged for multidisciplinary studies that use complementary computational and  experimental approaches to address challenging cancer research.
%下一篇文章的內容。目前在計畫中，但還沒有開始進行
These in vitro and in vivo validation experiments will be undertaken in Alex's laboratory (one of our co-authors).
We plan to analysis on mRNA (e.x. qRT-PCR) and protein (e.x. western blot) of HNSCC cell lysate to confirm expression of those candidate genes.
%mRNA expression level in HNSCC cell lines (其他文章已有發表 overexpression）
The effect of over-expression and knockdown of gene by lenti-viral clones should be observed on cell function assay (e.x. proliferation, migration, and invasion) and mouse xenograft model (e.x. tumor growth). %這些都需要一年以上的時間
%their rationale for looking into TMSB4X is not strongly supported by the available data.

This bioinformatics paper is providing targets and hints for the in vitro and in vivo validation.
We open invitation of research community by strongly support their rationale for looking into these HNSCC candidates.
%邀請科學家們一塊兒來繼續研究下去找出幫助癌症患者的方法
%the rest of the analysis seems fine, but 
%文章的初衷、跨領域：如同deep leaning Keras API，推廣研究者一個有效的方法 
We also aim to promote a reproducible research\cite{Preeyanon2014} with this workflow which will apply on their in-house HNSCC database to find more useful biomarkers. % or even other cancer types
why reproducibility?

Once those candidates are identified as the target, the compound screening could help to discover a potential drug for HNSCC therapy.
%https://www.mdpi.com/journal/cancers/instructions

%The authors should provide a separate Revision Notes file for revisions. The file should include a point-by-point response to each reviewer's comments, which the authors have received alongside the initial decision letter from the handling editor. Revision notes should clearly state the revisions the authors made to the manuscript, preferably including the subdivision title and page/line numbers to indicate where the manuscript has been edited.

% rebuttal
%Reconsider after Major Revisions: 
%The acceptance of the manuscript would depend on the revisions. The author needs to provide a point by point response or provide a rebuttal if some of the reviewer’s comments cannot be revised.

%All reviewer comments should be responded to in a point-by-point fashion.

%usually, only one round of major revisions is allowed. Authors will be asked to resubmit the revised paper within a suitable time frame, and the revised version will be returned to the reviewer for further comments.

\subsubsection*{Author Appeals for a rejection, in case}
%Authors may appeal a rejection by sending an e-mail to the Editorial Office of the journal. The appeal must provide a detailed justification, including point-by-point responses to the reviewers' and/or Editor's comments. The Managing Editor of the journal will forward the manuscript and related information (including the identities of the referees) to the Editor-in-Chief, Associate Editor, or Editorial Board member. The academic Editor being consulted will be asked to give an advisory recommendation on the manuscript and may recommend acceptance, further peer-review, or uphold the original rejection decision. A reject decision at this stage is final and cannot be reversed.

...

\subsection*{Material and Methods}

\subsubsection{Quantitative real-time PCR (qRT-PCR) analysis}
%\subsectionmark*{qRT-PCR analysis}

DKK1 mRNA expression in Hep-2 and 293T cell lines, as well as tumor tissues from 30 pairs of LSCC specimens and adjacent non-cancer specimens, were measured using qRT-PCR as described previously [3]. The primer sequences were as follows: DKK1 forward primer: 5'-TAGAGTCTAGAACGCAAGGATCT-3' and DKK1 reverse primer: 5'-CAAAAACTATCACAGCCTAAAGGG--3'; $\beta$-actin forward primer: 5'-TTGTTACAG GAAG TCCCTTGC C-3' and $\beta$-actin reverse primer: 5'-ATGCTATCACCTCCCC TGTGTG-3'. Relative mRNA levels were calculated based on the cycle threshold (Ct) values, according to the equation: 2–ÎCt [ÎCt = Ct (DKK1) – Ct (β-actin)]. 
All experiments were performed in triplicate.\cite{Shi2014}

由 HNSCC cell lysate 測出 qRT-PCR，DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1 表現高；ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN and NPB 表現低？

然後我收集 7 genes 的 primer sequence pairs
做 qPCR 證明在 HNSCC 口腔癌 cell lysate 中是多的。當成回答問題：experiment prove our discovered 7 (out of 20 )genes 是值得繼續探索下去。

qRT-PCR and western blot analyses

DKK1 mRNA expression in Hep-2 and 293T cell lines, as well as tumor tissues from 30 pairs of LSCC specimens and adjacent non-cancer specimens, were measured using qRT-PCR as described previously [3]. The primer sequences were as follows: DKK1 forward primer: 5′-TAGAGTCTAGAACGCAAGGATCT C-3′ and DKK1 reverse primer: 5′-CAAAAAC TATCACAGCCTAAAGGG-3′; β-actin forward primer: 5′-TTGTTACAG GAAG TCCCTTGC C-3′and β-actin reverse primer: 5′-ATGCTATCACCTCCCC TGTGTG-3′. Relative mRNA levels were calculated based on the cycle threshold (Ct) values, according to the equation: 2–ÎCt [ÎCt = Ct (DKK1) – Ct (β-actin)]. All experiments were performed in triplicate.

qRT-PCR primer design: primer sequence of
DKK1 forward primer: 5′-TAGAGTCTAGAACGCAAGGATCTC-3′
DKK1 reverse primer: 5′-CAAAAACTATCACAGCCTAAAGGG-3′

FaDu cells
STC2 forward primer: 5'-TGAAATGTAAGGCCCACGCT-3'
STC2 reverse primer: 5'-CGAGGTGCAGAAGCTCAAGA-3'

PGK1 (condition: 62dC, Ct 25)
PGK1 forward primer: 5'-CAAGAAGTGTGCTGAGGCTGTCAC-3'
PGK1 reverse primer: 5'-GCAGTGTCTCCACCACCTATGAT-3'

SURF4 forward primer: 5'-GAT CCC CTC AGC ACC TTC CTG GAG GAT TCA AGA GAT CCT CCA GGA AGG TGC-3'
SURF4  reverse primer: 5'-AGC TTT TCC AAA AAT CAG CAC CTT CCT GGA GGA TCT CTT GAA TTC TCC AGG AAG-3'

USP10
USP10  forward primer: 5'-AAATGCCACCGAACCTATCGGC-3'
USP10 reverse primer: 5'-CAGCCATTCAGACCGATCTGGA-3'
(https://www.origene.com/catalog/gene-expression/qpcr-primer-pairs/hp208343/usp10-human-qpcr-primer-pair-nm_005153)

FOXA2
FOXA2 forward primer: 5'-GGAACACCACTACGCCTTCAAC-3'
FOXA2 reverse primer: 5'-AGTGCATCACCTGTTCGTAGGC-3'

STIP1
STIP1 forward primer: 5'-ATCCTCAGCGTCCTCTTGG‐3′
STIP1 reverse primer: 5'-GGTGGAGGTGTTGCAATCTCTT‐3′
(https://onlinelibrary.wiley.com/doi/full/10.1002/gcc.22136)\cite{Cho2014}

\subsection*{Results}

\subsection*{Discussion}

@@

\subsubsubsection*{Analysis by web-tools}

@@

\subsubsubsection*{Review articles}
After discovering using our workflow, we also performed the literature review by Embase/Pubmed to find the evidence convincing to 7 of our suggested 20 biomarkers in cancer research.
%Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
%through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
%PubTator Central\cite{Wei2019} is a useful Pubmed text miner

>>>>

\section*{Response to Reviewer 3 Comments}
%Response to Referees} % rebuttal
We much appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point reply to the reviewer's comments are as follows (marked as \textcolor{blue}{blue}). 
Moreover, the revised portions in the manuscript are indicated in \textcolor{red}{red}.

\subsection*{3-1}
Comments from the reviewer \#3

%Must be improved:
%Is the research design appropriate?
%Are the results clearly presented?
Are the conclusions supported by the results?

@@

There is little information provided. The authors should provide more evidence to support this article.
%  Once the authors identify TMSB4X as a target, the rest of the analysis seems fine, but their rationale for looking into TMSB4X is not strongly supported by the available data.

@@

We appreciate the reviewer for the critical comment. We provide more evidence mentioned below to support the prognostic impact of these candidate genes. We summarized the conclusion below.

@@

\subsubsection*{Analysis by web-tools}

@@

\subsubsection*{Review articles}
After discovering using our workflow, we also performed the literature review by Embase/Pubmed to find the evidence convincing to 7 of our suggested 20 biomarkers in cancer research.
%Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
%through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.
%PubTator Central\cite{Wei2019} is a useful Pubmed text miner
